### 2019-10-01 uiuc.tex
grammar fixes

\subsubsection{Accessibility and Accomodation}
 A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year. CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app. Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and rideshare services are also plentiful. There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports. Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom. Holding a conference during this time would be the perfect way to showcase our beautiful city.

@@

\clearpage

@@

\subsubsection{NPRE Research Groups and Laboratories}
The faculty, pictured in Figure \ref{fig:faculty} support the above areas of 
expertise in the collaborations and facilites discussed below.

>>>>

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
airports, ground transportation to the Champaign area will be required. 
If flying into Chicago (ORD or MDW), attendees may choose to rent a car or take a bus to 
Champaign. The organizers recommend Peoria Charter in this case. Peoria Charter 
is a reliable bus company that offers several shuttles throughout the day from 
Chicago to the university. The Altgeld Hall Peoria bus stop is less than one block 
from the Illini Union and the TownePlace Suites.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature 
of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
weather and spring coming into bloom. Holding a conference during this time 
will be the perfect way to showcase our beautiful city.

@@

% \clearpage

@@

\subsubsection{Reliability and Risk Analysis}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{mohaghegh.jpg}
    \caption{Prof. Zahra Mohaghegh is an Assistant Professor in Nuclear, 
          Plasma, and Radiological Engineering and director of the 
          Socio-Technical Risk Analysis (SoTeRiA) Research Laboratory.}
  \end{center}
\end{wrapfigure}
Risk analysis represents the pinnacle of interdisciplinary research and education. Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States. Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA. It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
\subsubsection{NPRE Research Groups and Laboratories}
The faculty, pictured in Figure \ref{fig:faculty} support the above areas of 
expertise in the collaborations and facilites discussed below.
